# My first knitr document
Karel Machacek

## Loading and preprocessing the data

download the data, unzip them and plot the histogram

```{r}
# set working directory
setwd("C:\\private\\private_karel\\karel\\Coursera\\reproducible_research")
# set the URL for file download
fileURL="https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2Factivity.zip"
# download the zip file
#download.file(fileURL,"file.zip")
# unzip the zipfile
unzip("file.zip")
# list.files(".")
# read the zipfile
filecontent <- read.csv("activity.csv")
# just some debug code
# head(filecontent)
# tail(filecontent)
```
## What is mean total number of steps taken per day?
```{r}
# aggregate
agg_filecontent <- aggregate( steps ~ date, data = filecontent, FUN=sum, na.rm=TRUE)
# hisotgram of total steps taken per day
hist(agg_filecontent$steps, breaks=60)
```

print mean and median of steps taken each day
```{r}
# mean of steps taken each day
mean(agg_filecontent$steps)
# median of steps taken each day
median(agg_filecontent$steps)
```

## What is the average daily activity pattern?
plot the graph of steps per interval
```{r}
agg_filecontent2 <- aggregate ( steps ~ interval, data = filecontent, FUN = mean, na.rm = TRUE)
plot(agg_filecontent2$interval, agg_filecontent2$steps, type = "l")
```

print maximum number of average steps
```{r}
# interval with maximum number of average steps
sapply(agg_filecontent2, max, na.rm = TRUE)
```

## Imputing missing values
```{r}
# total number of NA values
sum(is.na(filecontent$steps))
```


## Are there differences in activity patterns between weekdays and weekends?

weekday
```{r}
filecontent$date2 = as.Date(filecontent$date, format = "%Y-%m-%d")
filecontent$weekday = weekdays(filecontent$date2)
# set weekends to weekend
filecontent[grep("S", filecontent$weekday),]$weekend="weekend"
# set weekdays to weekday
filecontent[grep("S", filecontent$weekday, invert=TRUE),]$weekend="weekday"
# weekday data plot
weekday = subset(filecontent, filecontent$weekend=="weekday")
#agg_weekday = aggregate( steps ~ interval, data = weekday, FUN = mean, na.rm = TRUE)
#plot(agg_weekday$interval, agg_weekday$steps, type = "l")
```

weekend
```{r}
# weekens data plot
weekend = subset(filecontent, filecontent$weekend=="weekend")
#agg_weekend = aggregate( steps ~ interval, data = weekend, FUN = mean, na.rm = TRUE)
#plot(agg_weekend$interval, agg_weekend$steps, type = "l")
```


